Propositions as Sessions, Mechanically

### 2015-04-08 paper/formalisation.tex
Added Coq code to be described.
Also removed dependency of paper folder on the proposal items.

Figure~\ref{fig:cll} presents the process calculus CP in LNCQ form with some
tedious details relating to environment uniqueness and ordering (see below)
elided. In other words, bound variables are represented using de Brujin
indices and free variables are represented using an abstract type provided by
the Metatheory library. The rules with binders reflect this by specifying the
type of a bound variable in the constructor rather than a name. Cofinite
quantification is performed in the hypotheses to these rules by excluding a
finite set of names from opening the subprocesses where opening a process $P$
with name $x$ is denoted $P^x$. Note that the rules for polymorphism,
$\exists$ and $\forall$, were not included in the final Coq development since
GV (\S~\ref{sec:gv}) does not support polymorphism making the rules
unnecessary for the translation. Further, as noted by \citeauthor{Lee:2012},
support for polymorphism in type variables creates an explosion of the
infrastructure requiring additional of opening and substituting definitions
and lemmas. They appear in the Figure simply for the sake of completeness.

@@

@@

The principal cut elimination rules are presented in Figure~\ref{??}. The
reduction rules were complicated to prove due to being composed of multiple
constructor instances and differ significantly to the standard operational
semantics one typically deals with in $\lambda$-calculus formalisms. As a
result, these well-typed reductions were not proved ``in-place'', instead each
rule is proved as a separate lemma. Most proofs followed a pattern but it was
difficult to automate satisfactorily for the reasons stated in the previous
paragraph. However, some tasks could be delegated to a custom tactic, for
example instantiating cofinitely quantified hypotheses with a newly introduced
fresh variable.

@@

Unfortunately, the reduction relation does not have knowledge of the
environment, $\Gamma$, typing process $\tm{P}$. This fact does not impact upon
expressing weakening because only the names (not the types in the bindings)
within the environment are required for weakening. one can compare alms with this version of cp
since it weakening rule corresponds to affine logic

@@

\input{cpstructeq}

\input{commconvonecp}

\input{commconvtwocp}

@@

\input{gv}

>>>>

Figure~\ref{fig:cll} presents the process calculus CP in LNCQ form with some
tedious details relating to environment uniqueness elided. In other words,
bound variables are represented using de Bruijn indices and free variables are
represented using an abstract type provided by the Metatheory library. The
rules with binders reflect this by specifying the type of a bound variable in
the constructor rather than a name. Cofinite quantification is performed in
the hypotheses to these rules by excluding a finite set of names from opening
the subprocesses where opening a process $P$ with name $x$ is denoted
$P^x$. Note that the rules for polymorphism, $\exists$ and $\forall$, were not
included in the final Coq development since GV (\S~\ref{sec:gv}) does not
support polymorphism making the rules unnecessary for the
translation. Further, as noted by \citeauthor{Lee:2012}, support for
polymorphism in type variables creates an explosion of the infrastructure
requiring additional of opening and substituting definitions and lemmas. They
appear in the Figure simply for the sake of completeness.

@@

\subsubsection{Subject Reduction Theorem}

The subject reduction theorem can be expressed in Coq as follows:
\begin{coq}
Theorem proc_sub_red:
  forall $\Gamma$ P Q
         (WT: P $\tpvdash_{cp}$ $\Gamma$)
         (RED: P $\becomes$ Q),
    Q $\tpvdash_{cp}$ $\Gamma$.
Proof. ii; gen $\Gamma$; induction RED; subst; eauto. Qed.
\end{coq}

\coqe$forall$ quantifies over hypotheses in the statement; everything before
the comma. \key{WT} and \key{RED} introduce names for the corresponding
hypotheses. The statement to prove is that if \coqe$P$ is a well-typed process
in a context $\Gamma$ and \coqe$P$ reduces to \coqe$Q$ then \coqe$Q$ is
well-typed in $\Gamma$. The proof environment is started using \coqe$Proof.$
and then followed by a sequence of tactics until all goals have a been
proven. After execution of \coqe$Qed.$ the Coq system inspects the validity of
the proof object constructed by the tactics and, if valid, will added the
theorem to the environment.

Some tactics used above are shorthands for commonly combined tactics, defined
using Ltac, a language for defining custom tactics and decision
procedures. For example, \coqe$ii$ repeatedly performs hypothesis introduction
then simplification until no more can be peformed, and \coqe$gen$ $\Gamma$
generalises the following induction over the environment $\Gamma$.

@@

The last step in the proof \coqe$eauto$ attempts to solve the goals generated
by the induction using lemmas known to the system. The goals to be proved
corresponding exactly to lemmas satisfying the reduction relation. The
reduction rules were complicated to prove due to being composed of multiple
constructor instances and differ significantly to the standard operational
semantics one typically deals with in $\lambda$-calculus formalisms. Most
proofs followed a pattern but it was difficult to automate satisfactorily for
the similar reasons stated for permutation automation. However, some tasks
could be delegated to a custom tactic, for example instantiating cofinitely
quantified hypotheses with a newly introduced fresh variable. An example of a
principal cut reduction statement in Coq is shown in Figure~\ref{principal}.
The hypothesis contains explicit de Bruijn

@@

Unfortunately, the reduction relation does not have knowledge of the
environment, $\Gamma$, typing process $\tm{P}$. This fact does not impact upon
expressing weakening because only the names (not the types in the bindings)
within the environment are required for weakening. Without contraction, this
version of CP corresponds to affine logic. alms calculus vs gv calculus w/o
contraction?

@@

%\input{cpstructeq}

%\input{commconvonecp}

%\input{commconvtwocp}

@@

%\input{gv}
